Rigid fluid coupling

### 2022-05-27 manuscript/paper.tex
Put dam breaking flow over rigid cubes figures in paper.

\Cref{fig:snapshots-single-cube-3d-dam-breaking-flow} shows the snapshots of
the rigid cube moving downstream of the tank when interacting with the fluid
flow against the experimental result (cite SPH DCDEM). From
\Cref{fig:snapshots-single-cube-3d-dam-breaking-flow} we can see that the
rigid cube matches well with the experimental result. Further, we compare the
positions of the rigid cube with time in
\Cref{fig:x-position-single-cube-3d-dam-breaking-flow}, against the
experimental results, SPH-DCDEM, MPS-DEM results. It can be seen from figure
\Cref{fig:x-position-single-cube-3d-dam-breaking-flow} that the current solver
is able to provide good accuracy in producing the correct displacement of the
cube and agrees well with the experimental as well as the other numerical
techniques.
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Snapshots of a single cube under a 3d dam breaking flow}
\label{fig:snapshots-single-cube-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{x position of the cube with time for single cube.}
\label{fig:x-position-single-cube-3d-dam-breaking-flow}
\end{figure}

The initial configuration of the dam breaking flow over three cubes is shown
in figure \Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}.
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} shows the snapshots of
the rigid cubes at different time instants from the start of fluid hit with
the color of the fluid particles representing pressure. From the
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} we can see that the
simulated rigid bodies match well with the experimental observations. We also
compare the x component of the effective center of mass of the three cubes
with time in \Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}, against
the experimental results, SPH-DCDEM, MPS-DEM results. From figure
\Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}, we can see that the
current solve is agrees well with the experimental as well as with the other
numerical method results.
\begin{itemize}
\item Mention at what time does the fluid hits the rigid cubes.
\end{itemize}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Snapshots of a three cubes under a 3d dam breaking flow}
\label{fig:snapshots-three-cubes-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{x position of the cubes with time for three cube.}
\label{fig:x-position-three-cubes-3d-dam-breaking-flow}
\end{figure}

The placement of the cubes in the pyramid configuration including dimensions,
distance from the left wall and other dimension related information can be
seen in figure \Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}.
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} shows the snapshots of
the rigid cubes at different time instants and the color coding of the fluid
particles represents pressure. From
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}, it can be seen that the
rigid body positions are in match with the experimental observations. Which is
further validated by doing a quantitative comparison of the x component of
effective center of mass of the six cubes in time against the experimental
results, SPH-DCDEM, MPS-DEM results in
\Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}. From these figures, we
can see that the current solver is in good agreement with the other numerical
and experimental results.
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Snapshots of six cubes under a 3d dam breaking flow}
\label{fig:snapshots-six-cubes-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{x position of the six with time for three cube.}
\label{fig:x-position-six-cube-3d-dam-breaking-flow}
\end{figure}

>>>>

\Cref{fig:snapshots-single-cube-3d-dam-breaking-flow} shows the snapshots of
the rigid cube moving downstream of the tank when interacting with the fluid
flow against the experimental result (cite SPH DCDEM). From
\Cref{fig:snapshots-single-cube-3d-dam-breaking-flow} we can see that the
rigid cube matches well with the experimental result. Further, we compare the
positions of the rigid cube with time in
\Cref{fig:x-position-single-cube-3d-dam-breaking-flow}, against the
experimental results, SPH-DCDEM, MPS-DEM results. It can be seen from figure
\Cref{fig:x-position-single-cube-3d-dam-breaking-flow} that the current solver
is able to provide good accuracy in producing the correct displacement of the
cube and agrees well with the experimental as well as the other numerical
techniques.
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Snapshots of a single cube under a 3d dam breaking flow}
\label{fig:snapshots-single-cube-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_one_cube_3d/case_1/xcom_vs_time}
  \caption{x position of the cube with time for single cube.}
\label{fig:x-position-single-cube-3d-dam-breaking-flow}
\end{figure}

The initial configuration of the dam breaking flow over three cubes is shown
in figure \Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}.
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} shows the snapshots of
the rigid cubes at different time instants from the start of fluid hit with
the color of the fluid particles representing pressure. From the
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} we can see that the
simulated rigid bodies match well with the experimental observations. We also
compare the x component of the effective center of mass of the three cubes
with time in \Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}, against
the experimental results, SPH-DCDEM, MPS-DEM results. From figure
\Cref{fig:x-position-three-cubes-3d-dam-breaking-flow}, we can see that the
current solve is agrees well with the experimental as well as with the other
numerical method results.
\begin{itemize}
\item Mention at what time does the fluid hits the rigid cubes.
\end{itemize}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Snapshots of a three cubes under a 3d dam breaking flow}
\label{fig:snapshots-three-cubes-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_three_stacked_cubes_3d/case_1/xcom_vs_time}
  \caption{x position of the cubes with time for three cube.}
\label{fig:x-position-three-cubes-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_three_stacked_cubes_3d/case_1/ycom_vs_time}
  \caption{y position of the cubes with time for three cube.}
\label{fig:y-position-three-cubes-3d-dam-breaking-flow}
\end{figure}

The placement of the cubes in the pyramid configuration including dimensions,
distance from the left wall and other dimension related information can be
seen in figure \Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}.
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow} shows the snapshots of
the rigid cubes at different time instants and the color coding of the fluid
particles represents pressure. From
\Cref{fig:snapshots-three-cubes-3d-dam-breaking-flow}, it can be seen that the
rigid body positions are in match with the experimental observations. Which is
further validated by doing a quantitative comparison of the x component of
effective center of mass of the six cubes in time against the experimental
results, SPH-DCDEM, MPS-DEM results in
\Cref{fig:x-position-six-cubes-3d-dam-breaking-flow}. From these figures, we
can see that the current solver is in good agreement with the other numerical
and experimental results.
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Snapshots of six cubes under a 3d dam breaking flow}
\label{fig:snapshots-six-cubes-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_six_stacked_cubes_3d/case_1/xcom_vs_time}
  \caption{x position of the cubes with time for six cubes.}
\label{fig:x-position-six-cubes-3d-dam-breaking-flow}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/amaro_2019_dam_breaking_flow_hitting_six_stacked_cubes_3d/case_1/ycom_vs_time}
  \caption{y position of the cubes with time for six cubes.}
\label{fig:y-position-six-cubes-3d-dam-breaking-flow}
\end{figure}
